ICM testing

### 2025-02-03 Scripts/archive/ASR_stocks.Rmd

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'D:/GitHub/ICM'

@@

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

@@

# Now we can run the figures separately.
# tuned.res <- readRDS(file = "D:/Github/ICM/Results/tuned_fits.Rds")
back.ts <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_summaries.Rds")
back.ts.quants <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_ts_quantiles_summaries.Rds")
back.res <- readRDS(file = "D:/Github/ICM/Results/backwards_sim_results.Rds")
load(file = "D:/Github/ICM/Results/model_inputs.Rdata")

for(i in Stocks)
{
  # Unpack the lists
  tunes <- tuned.res[[i]] 
  did.it.work <- back.ts[[i]] 
  quants <- back.ts.quants[[i]] 
  missing_rem <- mr.tmp[[i]] 
  tst <- back.res[[i]]

  did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"

    # All the results in a plot
  p2 <- ggplot() +
          geom_line(data=did.it.work, aes(x=years,y=abund,color=sim)) +
          xlab("") +
          ylab("Abundance (1000s)") +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) +
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)
  # Same thing but functional boxplots
  p3 <- ggplot() +
          geom_line(data=quants, aes(x=years,y= med)) +
          geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
          geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          xlab("") + ylab("Abundance (1000s)") +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + #geom_vline()
          ggtitle(i)+
          geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)

  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  p4 <- ggplot(tst$r) +
          geom_line(aes(x=years,y=r,group=n.sims,color=n.sims)) +
          xlab("") +
          ylab("Lotka r") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i)
  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/lokta_r_", i, ".png"), base_width = 6,base_height = 4)

  # Comparing our new time series with the old
  p2 <- ggplot() +
          geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
          xlab("") +
          ylab("Abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)

  # Comparing the absolute miss from the tuned time series
   p3 <- ggplot() +
          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.n),color='red') +
          xlab("") +
          ylab("Difference in abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) 
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)

  # What percentage (mean) difference
   p4 <- ggplot() +
          #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
          xlab("") +
          ylab("Difference in abundance (%)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)

     # Difference in m's
   p5 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=diff.m),color='red') +
          xlab("") +
          ylab("Difference in natural mortality (Instantaneous)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p5, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_m_", i, ".png"), base_width = 6,base_height = 4)
     # % Difference in m's
   p6 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
          xlab("") +
          ylab("Difference in natural mortality (%)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)

   p7 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=mn.m),color='blue') +
          geom_line(data=tunes$res[-1,], aes(x=year,y=vpa.m),color='black') +
          xlab("") +
          ylab("Natural mortality (Instantaneous)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p7, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Nat_M_", i, ".png"), base_width = 6,base_height = 4)

     p8 <- ggplot() +
          geom_line(data=tunes$res[-1,], aes(x=year,y=r),color='blue') +
          xlab("") +
          ylab("Lotka r") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p8, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/Lotka_r_", i, ".png"), base_width = 6,base_height = 4)

>>>>

```{r, load-stuff,echo=F, message=F, warning=F, fig.width=6, fig.height=4}
# OK, so using the ICES assessments here's what we get for North Sea cod.
library(readxl)
library(tidyverse)
library(rio)
library(ggthemes)
library(cowplot)
loc <- 'D:/GitHub/ICM'
loc <- "C:/Users/Owner/Documents/GitHub/ICM/"

@@

  #if(am.1s | am.0s | am.2s > 0) print("Stop, you need to check the age at maturity for either age 0 or 1 as there is data in there.")
  nat.mort <-  ASR_sub %>% dplyr::filter(type=="NM") %>% dplyr::rename(NM=value) %>% dplyr::select(-type)
  abund <- ASR_sub %>% dplyr::filter(type=="Num") %>% dplyr::rename(Num=value) %>% dplyr::select(-type)
  weight.age <- ASR_sub %>% dplyr::filter(type=="WA") %>% dplyr::rename(WA=value) %>% dplyr::select(-type)
  if(i == Stocks[30]) weight.age$WA <- weight.age$WA/1000
  removals <- ASR_sub %>% dplyr::filter(type=="Catch") %>% dplyr::rename(Catch=value) %>% dplyr::select(-type)

@@

# Now we can run the figures separately.
#tuned.res <- readRDS(file = paste0(loc,"/Results/tuned_fits.Rds"))
back.ts <- readRDS(file = paste0(loc,"/Results/backwards_sim_ts_summaries.Rds"))
back.ts.quants <- readRDS(file = paste0(loc,"/Results/backwards_sim_ts_quantiles_summaries.Rds"))
back.res <- readRDS(file = paste0(loc,"/Results/backwards_sim_results.Rds"))
for.res <- readRDS(file = paste0(loc,"/Results/forwards_sim_results.Rds"))
for.ts <- readRDS(file = paste0(loc,"/Results/forwards_sim_ts_summaries.Rds"))
for.ts.quants <- readRDS(file = paste0(loc,"/Results/forwards_sim_ts_quantiles_summaries.Rds"))

loc <- "C:/Users/Owner/Documents/Github/ICM"
load(file =  paste0(loc,"/Results/model_inputs.Rdata"))
load(file = paste0(loc,"/Results/all_cleaned_forward_tune_summaries_fec_nm.Rdata"))

Stocks <- unique(for.tunes$Stock)

for(i in Stocks)
{
  # Unpack the lists
 #tunes <- tuned.res[[i]] 
  did.it.work <- for.tunes |> collapse::fsubset(Stock == i) 
  #quants <- back.ts.quants[[i]] 
  #missing_rem <- mr.tmp[[i]] 
 # tst <- back.res[[i]]

  #did.it.work$missing[did.it.work$years %in% missing_rem] <- "missing"

    # All the results in a plot
  p2 <- ggplot() +
          geom_line(data=did.it.work, aes(x=year,y=est.abund),color='blue') +
          geom_line(data=did.it.work, aes(x=year,y=vpa.abund), color='black') +
          xlab("") +
          ylab("Abundance (1000s)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + scale_color_viridis_d(end = 0.75) +
          ggtitle(i) #+
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p2, filename = paste0(loc,"/Figures/tuned/", i, "/tuned_vs_vpa_", i, ".png"), base_width = 10,base_height = 8)
  # Same thing but functional boxplots
  # p3 <- ggplot() +
  #         geom_line(data=quants, aes(x=years,y= med)) +
  #         geom_ribbon(data=quants, aes(x=years,ymax=U.50,ymin = L.50),alpha=0.5,fill='blue',color='blue') +
  #         geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         xlab("") + ylab("Abundance (1000s)") +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + #geom_vline()
  #         ggtitle(i)+
  #         geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/raw/", i, "/runs_vs_vpa_ribbon_", i, ".png"), base_width = 6,base_height = 4)

  # Plotting how the estimate of r changes over time (which you can do when we have time varying inputs (e.g. Wgt, M, or maturity at age)
  p4 <- ggplot(did.it.work) +
          geom_line(aes(x=year,y=lambda)) +
          xlab("") +
          ylab("Lambda") +
          #scale_y_continuous(breaks = seq(0,1.5,by=0.1)) +
          #scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') +
          scale_color_viridis_c(end = 0.75) +
          ggtitle(i)
  save_plot(plot = p4, filename = paste0(loc,"/Figures/tuned/", i, "/lambda_", i, ".png"), base_width = 10,base_height = 8)

  # Comparing our new time series with the old
  # p2 <- ggplot() +
  #         geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
  #         geom_line(data=tunes$res, aes(x=year,y=vpa.n),color='black') +
  #         xlab("") +
  #         ylab("Abundance (1000s)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') +
  #         ggtitle(i) #+
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p2, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/tunded_vs_vpa_", i, ".png"), base_width = 6,base_height = 4)

  # Comparing the absolute miss from the tuned time series
  #  p3 <- ggplot(did.it.work) +
  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
  #         geom_line( aes(x=year,y=diff.n),color='red') +
  #         xlab("") +
  #         ylab("Difference in abundance (1000s)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) 
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p3, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/diff_N_", i, ".png"), base_width = 6,base_height = 4)

  # What percentage (mean) difference
  #  p4 <- ggplot() +
  #         #geom_line(data=tunes$res, aes(x=year,y=lotka.n),color='blue') +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.n),color='red') +
  #         xlab("") +
  #         ylab("Difference in abundance (%)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) #+ ylim(c(-100,100))
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p4, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_N_", i, ".png"), base_width = 6,base_height = 4)

     # Difference in m's
   p5 <- ggplot(did.it.work) +
          geom_line( aes(x=year,y=mean.nm),color='blue') +
          geom_line( aes(x=year,y=mean.vpa.nm),color='black') +
          xlab("") +
          ylab("Natural mortality (Instantaneous)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p5, filename = paste0(loc,"/Figures/tuned/", i, "/Nat_mort_", i, ".png"), base_width = 10,base_height = 8)
     # % Difference in m's
  #  p6 <- ggplot() +
  #         geom_line(data=tunes$res[-1,], aes(x=year,y=per.diff.m),color='red') +
  #         xlab("") +
  #         ylab("Difference in natural mortality (%)") +
  #         #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
  #         #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
  #         theme_few() + theme(legend.position = 'none') + 
  #         ggtitle(i) #+ ylim(c(-100,100))
  #         #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  # save_plot(plot = p6, filename = paste0("D:/Github/ICM/Figures/tuned/", i, "/per_diff_m_", i, ".png"), base_width = 6,base_height = 4)

    p6 <- ggplot(did.it.work) +
          geom_line( aes(x=year,y=mean.fec),color='blue') +
          geom_line( aes(x=year-1,y= mean.vpa.fec),color='black') +
          xlab("") +
          ylab("Recruits (Number) per spawner (kg female)") +
          #geom_line(data=did.it.work %>% dplyr::filter(sim == "VPA"),aes(x=years,y=abund),color='black',size=2) +
          #scale_y_continuous(breaks = seq(0,3e6,by=5e5)) + scale_x_continuous(breaks = seq(1960,2025,by=5)) +
          theme_few() + theme(legend.position = 'none') + 
          ggtitle(i) #+ ylim(c(-100,100))
          #geom_text(data=did.it.work[did.it.work$missing=="missing",], aes(x=years, y=abund, label="?"))
  save_plot(plot = p6, filename = paste0(loc,"/Figures/tuned/", i, "/Fecundity_", i, ".png"), base_width = 10,base_height = 8)

### 2025-02-03 Scripts/archive/Paper_1.Rmd

>>>>

# Download the functions we'll need from github
  funs <- c("https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/simple_Lotka_r.r",
            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/backwards_project.r",
            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/forward_project.r",
            "https://raw.githubusercontent.com/dave-keith/ICM/main/Scripts/functions/tuning_sim_fast.R",

  )
  # Now run through a quick loop to load each one, just be sure that your working directory is read/write!
  for(fun in funs) 
  {
    download.file(fun,destfile = basename(fun))
    source(paste0(getwd(),"/",basename(fun)))
    file.remove(paste0(getwd(),"/",basename(fun)))
  }
